Presentation Title

### 2017-08-09 thesis/chapters/ch3-model.tex
Change code URL, etc.

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties may look like Byzantine consensus properties (which we describe next in \Cref{sec:acs-background}) but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

@@

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with a non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $C$, then every node outputs $C$.
    \item \emph{Validity:}
        If any correct node outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ nodes.
    \item \emph{Totality:}
        If $n - t$ nodes receive an input, then all correct nodes produce an output.
\end{enumerate}
\end{definition}

@@

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.
The probability that an honest node catches out a malicious node is 
$$p = \frac{f}{r},$$
where $f$ is the number of bad agreed fragments and $r$ is the latest round number.
If there are more nodes (say $n$) trying to make transactions with the malicious node,
then the probability that the malicious node gets caught at least once (denoted by the random variable $X$) follows a binomial distribution, i.e.
$$\Pr[X > 0] = \sum_{k = 1}^{n}\binom{n}{k}p^k (1 - p)^{n - k}.$$

>>>>

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties are similar to Byzantine consensus properties (which we describe next in \Cref{sec:acs-background}), but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

@@

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with a non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $C$, then every node outputs $C$.
    \item \emph{Validity:}
        If any correct node outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ nodes.
    \item \emph{Termination:}
        If $n - t$ nodes receive an input, then all correct nodes produce an output.
\end{enumerate}
\end{definition}

@@

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.

The probability that an honest node catches out a malicious node is 
$$p = \frac{f}{r},$$
where $f$ is the number of bad agreed fragments and $r$ is the latest round number.
If there are more nodes (say $n$) trying to make transactions with the malicious node,
then the probability that the malicious node gets caught at least once (denoted by the random variable $X$) follows a binomial distribution, i.e.
$$\Pr[X > 0] = \sum_{k = 1}^{n}\binom{n}{k}p^k (1 - p)^{n - k}.$$

### 2017-08-09 thesis/chapters/ch4-analysis.tex
Change code URL, etc.

Our last study considers the effect when the number of adversaries is more than $t$.
This is useful because in practice it is difficult to guarantee that $t$ satisfied $n \ge 3t + 1$, especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.

@@

On the other hand, due to the fact that hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric},
the probability for picking more than $\lfloor \frac{n-1}{3} \rfloor$ black balls when 
the expected value is much smaller than $\lfloor \frac{n-1}{3} \rfloor$ is small.
We can use tail inequality to bound the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ black balls when only $n\alpha$ are black where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor / n$.
The tail inequality is
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
where $E[X] = n\alpha$.
We are interested in $\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]$, so
\begin{align*}
\tau &= \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha
\end{align*}
Putting $\tau$ back into the tail inequality we get the following bound.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}
$$

>>>>

Our last study considers the effect when the number of adversaries is more than $t$.
This is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.

@@

On the other hand, due to the fact that hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric},
the probability for picking more than $\lfloor \frac{n-1}{3} \rfloor$ black balls when 
the expected value is much smaller than $\lfloor \frac{n-1}{3} \rfloor$ is small.
We can use tail inequality to bound the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ black balls when only $n\alpha$ are black where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor / n$.
The tail inequality is
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
where $E[X] = n\alpha$.
We are interested in $\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]$, so
$$
\tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha
$$
Putting $\tau$ back into the tail inequality we get the following bound.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}
$$
